\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-07 popl-2019-journal-v/paper.tex
[POPLjv] Add reference to micro-policy linear capabilities

In addition to the already-mentioned work on linear capabilities, \citet{van_strydonck_linear_2019} have recently used them in a secure (fully abstract) compiler for a C-like language with separation logic contracts.
A form of linear capabilities was also used in the SAFE machine developed within the CRASH/SAFE project \citep{DBLP:conf/sp/AmorimDGHPST15,DBLP:journals/jcs/AmorimCDDHPPPT16}.

>>>>

In addition to the already-mentioned work on linear capabilities, \citet{van_strydonck_linear_2019} have recently used them in a secure (fully abstract) compiler for a C-like language with separation logic contracts.
A form of linear capabilities was also used in the SAFE machine developed within the CRASH/SAFE project \citep{DBLP:conf/sp/AmorimDGHPST15,DBLP:journals/jcs/AmorimCDDHPPPT16}.
\citet{Abate:2018:GCG:3243734.3243745} used micro-policy enforced linear return capabilities to ensure a cross-component stack discipline.
Their linear capabilities were designed specifically to enforce the stack discipline but behave similarly to ours with the notable difference that their linear return pointers are destroyed in a jump.
